SunPy - Python for Solar Physics

### 2014-01-23 3-5-Database.tex
removed undo/redo code snippet

The need for a database package arose because using VSO alone lead to two major
problems:
\begin{enumerate}
  \item downloaded data cannot be queried or browsed
  \item to fetch data that has already been saved on the local hard drive,
    the VSO has to be queried again
\end{enumerate}

@@

In code listing \ref{code:db_3} the entries with the IDs \#1 -- \#3 have been
removed because they have been added first and are therefore the entries that
have been used least recently. To undo this operation, the \texttt{undo} method
is used in code listing \ref{code:db_4} to add the 3 removed entries back to
the database. The \texttt{redo} method removes them again.

\begin{listing}
\begin{minted}{python}
>>> database.undo()
>>> len(database)
6
>>> database.redo()
>>> len(database)
3
\end{minted}
\caption{Undoing and redoing operations.}
\label{code:db_4}
\end{listing}

% TODO: 'clever fetching'

>>>>

The need for a database package arose because using VSO alone led to two major
problems:
\begin{enumerate}
  \item downloaded data cannot be queried or browsed
  \item to fetch data that has already been saved on the local hard drive,
    the VSO has to be queried again
\end{enumerate}

@@

In code listing \ref{code:db_3} the entries with the IDs \#1 -- \#3 have been
removed because they have been added first and are therefore the entries that
have been used least recently.
